### 2023-06-13 Article.Rmd
1

>>>>

This research has limitations due to the use of secondary data obtained from platforms, suggesting future studies could benefit from primary data collection. Moreover, this study did not associate Engagement Rate (ER) with significant concurrent events, potentially overlooking the impact of emotional reactions based on these events. Future studies could explore these associations to understand emotional impacts better, thus extending the existing knowledge in the field.
